Chemically Dependent Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-04-13 Ben_Manuscripts/transport/Draft.tex
Comments on abstract/intro.

\title{Chemically Dependent Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\author{Michael R. Shirts}
\email{michael.shirts@colorado.edu}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}

@@

  The uniform size and complex chemical topology of the pores that 
  constitute cross-linked inverted hexagonal (H\textsubscript{II})
  phase lyotropic liquid crystal (LLC) membranes make them promising
  for selective separations. In this work, we observe transport
  of water, sodium ions and 20 small polar solutes within the pores 
  of an LLC membrane using atomistic molecular simulations. We found
  that the transport rate of a species is dependent not only on 
  molecular size, but on chemical functionality as well. The 
  membrane's inhomogeneous composition gives rise to radially dependent
  transport mechanisms with respect to the pore centers. In general, we 
  observed that all solutes perform intermittent hops between lengthy
  periods of entrapment. Three different trapping mechanisms are 
  responsible for this behavior. First, solutes that drift
  out of the pore can become entangled among the dense monomer
  tails. Second, solutes can donate hydrogen bonds to the monomer
  head groups. Third, solutes can coordinate with sodium counter ions.
  The degree to which a solute is affected by each mechanism is 
  dependent on the chemical functionality of the solute. Using the
  insights developed in this study, we can begin to think about 
  how to redesign existing LLC membranes in order to perform 
  solute-specific separations.

@@

  Membranes capable of separating nm-sized solutes with high selectivity 
  and permeability are highly desirable for a number of applications. For 
  example, separation of salt from seawater or other briny sources can 
  yield potable drinking water.\cite{fritzmann_state---art_2007} Removal
  of organic micropollutants, such as personal care products, pesticides
  and pharmaceuticals, from surface and groundwaters, can have large benefits
  for public health.\cite{schwarzenbach_challenge_2006} Finally,
  one can purify and recover dissolved species present in complex
  hydraulic fracturing flowback water waste streams which would help mitigate
  the effects of deep well injection and generate value.\cite{dischinger_application_2017} 
  %BJC: could make last point more general

%  All of these separations are possible with current commercial membrane
%  separation techniques but they are too energy intensive to be worth the 
%  capital investment needed to start the processes  
  All of these separations are possible with current commercial membrane
  separation techniques but suffer from serious drawbacks. Currently, reverse 
  osmosis (RO) and nanofiltration (NF) dominate commercial membrane separations
  of small molecules.\cite{warsinger_review_2018} RO membranes are typically
  dense polymer matrices that separate solutes based on differences in their
  solubility and permeability in the membrane material.\cite{fritzmann_state---art_2007}
  Although they can perform highly selective separations, high feed pressures,
  and thus large amounts of energy, are necessary in order to generate a 
  useful permeate flux.\cite{van_der_bruggen_review_2003} NF membranes have 
  well-defined nm-sized pores which can give the same permeate flux as RO
  with lower applied pressure.\cite{hilal_comprehensive_2004} However, the 
  pores are not uniform in size, limiting selectivity.\cite{werber_materials_2016}.
%  Therefore, multiple membrane passes may be necessary in order to achieve 
%  high selectivity.

@@

  Cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membranes are nanostructured membranes that may be able to achieve the
  selectivity of RO membranes while maintaining the high permeability
  of NF membranes.\cite{zhou_supported_2005} The H\textsubscript{II} LLC
  phase is formed when LLC monomers self-assemble into hexagonally packed
  and uniform-sized pores.\cite{smith_ordered_1997} Alignment and subsequent
  cross-linking of the hexagonal mesophases yields a mechanically strong
  membrane.\cite{feng_scalable_2014,feng_thin_2016} The uniform-sized pores
  enforce a strict molecular-size cut-off while the hexagonal geometry is 
  ideal for high permeability.\cite{zhou_supported_2005} Additionally, 
  because the LLC monomers are salts, Donnan exclusion plays a role in 
  rejection of charged molecules upon pore entry.\cite{donnan_theory_1995}
%  Zhou et al. demonstrated complete rejection
%  of solutes larger than 1.2 nm in size for H\textsubscript{II} LLC coated
%  membranes.\cite{zhou_supported_2005}

  In addition to geometric factors which make H\textsubscript{II} membranes
  ideal for selective separations, they have the potential to further disrupt
  conventional membrane separation techniques by being selective based not
  only on solute size and charge, but on chemical functionality as well. 
  The functional LLC monomer head groups that occupy the pore region of the
  membrane can interact with solutes. Dischinger et al. studied the 
  performance of a Q\textsubscript{I} phase LLC membrane, which has a 
  similar pore topology to the H\textsubscript{II} phase, but a more 
  tortuous geometry, and observed a range of selectivities dependent on the
  anion coordinated to the LLC monomer.\cite{dischinger_effect_2017} Intelligent 
  design of LLC monomers can help us tailor membranes for solute-specific
  separations.

  While H\textsubscript{II} membranes have been synthesized and characterized
  in a lab setting, there is a limit to the level of detail that can be obtained 
  from experiment. The separation performance of these membranes has been 
  primarily characterized with size-exclusion experiments which emphasizes 
  selectivity based on the ability to enter a given pore.\cite{zhou_supported_2005}
  While size-exclusion is a useful separation, it cannot reliably purify a 
  solution where the solute size is on the same order as water. Therefore, it is
  important to take advantage of material properties other than pore size. 
  Unfortunately, the complexity of LLC Membranes has obscured the interpretation
  of experimental transport studies.\cite{dischinger_effect_2017}  % BJC: ref to Sarah?

  Molecular dynamics (MD) simulations can give us mechanistic insights with 
  atomistic resolution so that we can directly observe small solute transport
  within LLC membrane nanopores and intelligently design new membranes for 
  solute-specific separations.

  In our previous work, we used MD simulations to determine the most likely 
  structure of the hexagonal phase formed by the monomer Na-GA3C11, expanding 
  upon the most recent experimental characterization.\cite{coscia_understanding_2018,feng_thin_2016}
  We developed techniques for equilibrating the hexagonal phase formed by neat 
  monomer as well as with varying amounts of water in the pores.

@@

  \end{tcolorbox}
  \caption{}\label{table:abbreviations}
  \end{table}

  First, we will comment on the membrane's structure. Previously, we have
  studied dry membrane systems and some systems with low water content. 
  We will observe how the radial density of monomer components and water 
  change based on membrane water content.

  % BJC: I don't really explicity comment on the partitioning of solutes
  % out of the pore. Maybe I can add some sort of chart. Need to think more.
  Then we will present our efforts to understand how small molecules, 
  including water, partition within the pores. From a macroscopic perspective,
  it is straightforward to hypothesize that the water and polar solutes spend
  their time exclusively in the tube-like hydrophilic pore region. Our
  previous work showed that there is a gradual compositional transition from
  the hydrophilic to the hydrophobic region which means that solutes may not
  necessarily stay confined to the centers of the pores or even within the 
  pore region. We will study the gradient in composition of solutes and 
  water and any resultant influence it might have on mechanistic properties.

  Finally, and for the bulk of this work, we will present our observations 
  and explanations of the observed transport mechanisms exhibited by water
  and solutes. Given that the pores will restrict motion of the solutes, we
  anticipate that transport will be hindered in some way. We want to understand
  the differences in solute motion, specifically its mean squared displacement 
  (MSD), based on a solute's size, shape and chemical functionality. We will 
  study the interactions between solutes, the membrane, and water in order to
  determine which mechanism or mechanisms dominate.

@@

  Stable H\textsubscript{II} phases, assembled with Na-GA3C11, can be formed
  using a broad range of water concentrations. In the literature, the system 
  studied in this work is typically synthesized with close to 10 wt \% water.
  \cite{smith_ordered_1997, zhou_new_2007} However, Resel et al. noted that the
  system is likely fully hydrated with less than 7 wt \% water.\cite{resel_h2-phase_2000}
  Excess water fills space between hexagonal mesophases. We decided to test 
  systems with two different water contents: 5 and 10 wt \%.

  We observed that water partitions into the distal tail region of our system and therefore
  built our initial configurations with water in both regions, close to the expected
  equilibrium partition. We define the distal tail region to be ca. 1.5 nm from the pore
  center based on the minimum in the radial distribution of water
  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
  may or may not be experimentally consistent but it is necessary for our results to be 
  thermodynamically consistent. We iteratively adjusted the pore radius in our systems
  until the appropriate amount of water fit in the pores after running the GROMACS command
  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
  in random locations with a short energy minimization between each insertion. When 
  studying transport of water in the pores, we limited the calculations to water molecules
  that spent greater than 95 \% of their time outside of the distal tail region.

@@

  The $z$-direction MSD of water in the 10 wt \% system is linear. Therefore, for
  the purpose of comparison, we calculated its diffusion constant by fitting a line
  to the linear region of the MSD curve.~\cite{maginn_best_2018}. The diffusion constant
  is then equal to $m/2$ where $m$ is the slope of the linear fit. The slope is divided
  by 2 (rather than 6) because we only measured the diffusion coefficient in one 
  dimension.

@@

  Since we will be using this equation for primarily qualitative observations, 
  we made a number of simplifying assumptions so that it could easily be used for 
  comparison between systems. First, we assume that all systems' viscosities
  are equal since we only make minor changes to the membrane's composition and
  accurately assessing the viscosity in a complex and inhomogeneous system such 
  as ours is a challenge by itself. Second, we assume all particles are approximately
  spherical, neglecting the effect of solute shape on mobility. Chan et al. 
  showed that the difference in diffusion constants of differently shaped 
  particles, with constant molecular volume, did not differ by more than 25 \%
  with most deviating by less than 10 \%.~\cite{chan_effects_2015}. 
  Third, we assume that the ratio of solute and solvent radii as calculated using the
  methodology of Section~\ref{method:molecular_size}, is equivalent to the the 
  ratio of hydrodynamic radii. For similarly shaped molecules, it has been shown that
  one can relate the hydrodynamic radius and radius of gyration (R\textsubscript{g})
  using a constant scaling factor. \cite{lee_molecular_2008,he_novel_2003,li_critical_2009}.
  % BJC: could just calculate Rg instead of end-to-end
  Assuming that our end-to-end distance reasonably approximates R\textsubscript{g} 
  for our small, relatively inflexible molecules, we believe this assumption is 
  justified for qualitative demonstrations relevant to this study.

@@

  Using our procedure we found that sodium ions in a solution of tip3p water
  coordinate with an average of 3.6 water molecules. We created a 4 x 4 x 4
  nm cubic box of water with the GROMACS tool, \texttt{gmx solvate}. We used
  \texttt{gmx genion} to replace water molecules with sodium and chloride 
  ions in order to create a 0.1 M NaCl solution. We let the system simulate
  for 5 ns and reported the average number of coordinated water molecules 
  per frame after discarding the first nanosecond of simulation.

@@

  We measured the average radial distance of each solute of interest 
  from the pore centers. We binned the radial distances and then 
  normalized by the volume of the annulus defined by the bin edges.
  Although the pores are often described as straight, they have a
  small degree of tortuosity which disrupts the RDF calcuation. We 
  tried to mitigate the effects of tortuosity by calculating the RDF
  with respect to splines that run through the pore centers. See
  Section~\ref{S-section:splines} of the Supporting Information for 
  a graphical illustration. Each spline consists of 10 points, equally
  spaced in the $z$-direction, whose ($x$, $y$) coordinates are defined
  based on the center of mass of all head groups closest, in $z$, to the
  given point. When calculating RDFs, the radial distance from the pore 
  center is based on the distance between the solute center-of-mass and
  the linearly interpolated ($x$, $y$) coordinates of the pore center 
  calculated based on the closest two spline points. Using the splines, 
  % BJC: below to supporting?
  we calculated the tortuosity of the pores by calculating the ratio 
  $\dfrac{L}{Z}$ where $L$ is the length of the spline and $Z$ is the 
  length of the unit cell in the $z$-direction. The average tortuosity
  of each pore is 1.03 $\pm$ 0.01 and 1.07 $\pm$ 0.02 in the 5 and 10 wt \%
  water systems respectively.

  In all RDF plots, we include the average RDF of the head groups as
  a reference. The head group RDF shown is the average of the head 
  group RDFs for each solute system in the plot. We generated 
  95 \% confidence intervals by bootstrapping the RDF of each individual
  head group. For each head group, we obtained an RDF averaged over the
  entire simulation trjaectory. We randomly chose head group RDFs with replacement
  and averaged them for each bootsrap trial. This approach assumes that
  head group positions are uncorrelated.

@@

  In contrast to our previous work with a dry version of this 
  membrane, the pore region of the 5 and 10 wt \% water 
  systems are primarily filled with water and sodium ions. We define the
  pore region based on the average COM position of the monomer head groups' 
  % BJC: not sure the best place in paper to define pore region. Maybe a system definitions section in Methods.
  % BJC: need to decide on exact definition. Should probably be the same as the 'Head Groups' line
  carboxylate oxygen atoms. Figure~\ref{fig:component_densities} plots the RDF of each membrane
  constituent in the dry system as well as the 5 and 10 wt \% water systems. 
  In dry systems, the pore center is densely filled with sodium ions and head
  groups. The peak head group density occurs within 0.25 nm of the pore center.
  In hydrated systems, water occupies, and is densest, at the center of each 
  pore. The density of sodium ions is somewhat uniform in the pore center of
  the 5 wt \% water system while it shows a maximum closer to the head groups
  in the 10 wt \% water system. The peak density of sodium ions is not at the
  pore center in the 10 wt \% water system likely because they are still
  loosely associated with the monomer's carboxylate head groups.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_dry.pdf}
  %BJC: simulation is extended to smooth out these curves
  \caption{Dry System}\label{fig:component_density_dry}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \vspace{-0.5cm}
  \includegraphics[width=\textwidth]{monomer_color_coded.pdf}
  \label{fig:monomer_color_coded}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}
  \caption{The radial densities of various monomer components paint a 
  picture of the pore topology where the pore centers are primarily composed
  of water and sodium ions. The monomer groups labeled in each plot correspond to 
  the color-coded monomer pictured in the upper right corner of the figure. 
  All RDFs represent the number of atoms located at a given distance from the
  pore center normalized by the volume of the annular bin to which they belong.
  (a) In the dry system, the density of head groups and sodium ions are highest
  within 0.25 nm of the pore center. (b) In the 5 wt \% system, monomer head 
  groups retreat about 0.2 nm radially in order to make room for water molecules.
  (c) Monomers in the 10 wt \% system retreat an additional 0.2 nm to make room
  for more water.}\label{fig:component_densities}
  \end{figure}

  There is an appreciable amount of water that partitions into the distal tail
  region of both systems. 28 \% and 31 \% of the total water is present in the tail
  regions of the 5 and 10 wt\% water systems respectively. See 
  Section~\ref{S-section:water_content_equil} of the Supporting Information for more details. This 
  result is due to a combination of the lower density of the tail region
  as well as oxygen atoms at the ends of each monomer tail which can further 
  stabilize water molecules. See Figure~\ref{S-fig:total_density} of the 
  Supporting Information for a graphical illustration of this point.

@@

  Water and sodium's mobilities increase in larger and less crowded pores. 
  In the 10 wt\% water system, the MSD of water is about 51 times higher and
  the MSD of sodium is about 49 times higher compared to the 5 wt \% water system. 
  In the 10 wt \% water system, water moves about 51 times faster than sodium 
  and in the 5 wt \% system, water moves about 49 times faster than sodium. Assuming
  long timescale Brownian behavior of water in the 10 wt \% system, we measured its
  diffusivity to be 7.45e-07 $cm^2 / s$ which is only 1.4 \% that of bulk tip3p 
  water.~\cite{mahoney_diffusion_2000} %BJC: 7.45e-07 versus 5.19e-05 cm^2/s

>>>>

%MRS2: ``dependent -> selective?'' 
\title{Chemically Dependent Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\author{Michael R. Shirts}
\email{michael.shirts@colorado.edu}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}

%MRS2: I think it would be useful to have a picture of the pores to
% allow people to visualize what was going on.  ToC might be good, 
% but I think that as people read, they need to see the 3D picture as well to think through things.

@@

  The uniform size and complex chemical topology of the pores that 
  constitute cross-linked inverted hexagonal (H\textsubscript{II})
  phase lyotropic liquid crystal (LLC) membranes make them promising
  for selective separations. In this work, we observe transport
  of water, sodium ions and 20 small polar solutes within the pores 
  of an LLC membrane using atomistic molecular simulations. We 
  %MRS2: 
  find
  %found
  %MRS2: ``transport rate -> transport''
  that the transport rate of a species is dependent not only on 
  molecular size, but on chemical functionality as well. The 
  membrane's inhomogeneous composition gives rise to radially dependent
  transport mechanisms with respect to the pore centers. In general, we 
  observed that all solutes perform intermittent hops between lengthy
  periods of entrapment. Three different trapping mechanisms are 
  responsible for this behavior. First, solutes that drift
  out of the pore can become entangled among the dense monomer
  tails. Second, solutes can donate hydrogen bonds to the monomer
  head groups. Third, solutes can coordinate with sodium counter ions.
  The degree to which a solute is affected by each mechanism is 
  dependent on the chemical functionality of the solute. Using the
  insights developed in this study, we can begin to think about 
  how to redesign existing LLC membranes in order to perform 
  solute-specific separations.

@@

  Membranes capable of separating nm-sized solutes with high selectivity 
  and permeability are highly desirable for a number of applications. For 
  example, separation of salt from seawater or other briny sources can 
  yield potable drinking water.~\cite{fritzmann_state---art_2007} Removal
  of organic micropollutants, such as personal care products, pesticides
  and pharmaceuticals, from surface and groundwaters, can have large benefits
  for public health.~\cite{schwarzenbach_challenge_2006} Finally,
  one can purify and recover dissolved species present in complex
  hydraulic fracturing flowback water waste streams which would help mitigate
  the effects of deep well injection and generate value.~\cite{dischinger_application_2017} 
  %BJC: could make last point more general
  %MRS2: ``generate value'' is pretty vague, yeah.

%  All of these separations are possible with current commercial membrane
%  separation techniques but they are too energy intensive to be worth the 
%  capital investment needed to start the processes  
% MRS2: maybe ``are possible'' -> ``are possible in part''?  Otherwise, it logically follows that they shouldn't have major drawbacks.
  All of these separations are possible with current commercial membrane
  separation techniques but suffer from serious drawbacks. Currently, reverse 
  osmosis (RO) and nanofiltration (NF) dominate commercial membrane separations
  of small molecules.~\cite{warsinger_review_2018} RO membranes are typically
  dense polymer matrices that separate solutes based on differences in their
  solubility and permeability in the membrane material.~\cite{fritzmann_state---art_2007}
  Although they can perform highly selective separations, high feed pressures,
  and thus large amounts of energy, are necessary in order to generate a 
  useful permeate flux.~\cite{van_der_bruggen_review_2003} NF membranes have 
  well-defined nm-sized pores which can give the same permeate flux as RO
  with lower applied pressure.~\cite{hilal_comprehensive_2004} However, the 
  pores are not uniform in size, limiting selectivity.~\cite{werber_materials_2016}.
%  Therefore, multiple membrane passes may be necessary in order to achieve 
%  high selectivity.

@@

  Cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membranes are nanostructured membranes that may be able to achieve the
  selectivity of RO membranes while maintaining the high permeability
  of NF membranes.~\cite{zhou_supported_2005} The H\textsubscript{II} LLC
  phase is formed when LLC monomers self-assemble into hexagonally packed
  and uniform-sized pores.~\cite{smith_ordered_1997} Alignment and subsequent
  cross-linking of the hexagonal mesophases yields a mechanically strong
  membrane.~\cite{feng_scalable_2014,feng_thin_2016} The uniform-sized pores
  enforce a strict molecular-size cut-off while the hexagonal geometry is 
  ideal for high permeability.~\cite{zhou_supported_2005} Additionally, 
  because the LLC monomers are salts, Donnan exclusion plays a role in 
  rejection of charged molecules upon pore entry.~\cite{donnan_theory_1995}
%  Zhou et al. demonstrated complete rejection
%  of solutes larger than 1.2 nm in size for H\textsubscript{II} LLC coated
%  membranes.~\cite{zhou_supported_2005}

  In addition to geometric factors which make H\textsubscript{II} membranes
  ideal for selective separations, they have the potential to further disrupt
  conventional membrane separation techniques by being selective based not
  only on solute size and charge, but on chemical functionality as well. 
  The functional LLC monomer head groups that occupy the pore region of the
  membrane can interact with solutes. Dischinger et al.~studied the 
  performance of a Q\textsubscript{I} phase LLC membrane, which has a 
  similar pore topology to the H\textsubscript{II} phase, but a more 
  tortuous geometry, and observed a range of selectivities dependent on the
  anion coordinated to the LLC monomer.~\cite{dischinger_effect_2017} Intelligent 
  design of LLC monomers can help us tailor membranes for solute-specific
  separations.

  While H\textsubscript{II} membranes have been synthesized and characterized
  in a lab setting, there is a limit to the level of detail that can be obtained 
  from experiment. The separation performance of these membranes has been 
  primarily characterized with size-exclusion experiments which emphasizes 
  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
  While size-exclusion is a useful separation, it cannot reliably purify a 
  solution where the solute size is on the same order as water. Therefore, it is
  important to take advantage of material properties other than pore size. 
  %MRS2: is ``complexity'' the right word? Can we be more specific?
  Unfortunately, the complexity of LLC membranes has obscured the interpretation
  of experimental transport studies.~\cite{dischinger_effect_2017}  % BJC: ref to Sarah?

  %MRS2: odd to have a one sentence paragraph?  MAyber just join with the next paragraph.
  Molecular dynamics (MD) simulations can give us mechanistic insights with 
  atomistic resolution so that we can directly observe small solute transport
  within LLC membrane nanopores and intelligently design new membranes for 
  solute-specific separations.

  In our previous work, we used MD simulations to determine the most likely 
  structure of the hexagonal phase formed by the monomer Na-GA3C11, expanding 
  upon the most recent experimental characterization.~\cite{coscia_understanding_2018,feng_thin_2016}
  We developed techniques for equilibrating the hexagonal phase formed by neat 
  monomer as well as with varying amounts of water in the pores.

@@

  %MRS2: can you put molecules in the table as well? I think it would be better for reference. Some of the larger ones may have small molecules.  You can potentially partially stagger them horizontally so the size can be OK? 
  \end{tcolorbox}
  \caption{}\label{table:abbreviations}
  \end{table}

  %MRS2: generally, use present tense for what is being done in the paper, not future tense; 
  %the paper is completely written, later sections are not being written in the future. 
  %MRS2: descriptions of experiements can be in the past.   
  %First, we will comment on the membrane's structure. 
  We first address the structure of the pores formed in the membrane.
  Previously, we have
  studied dry membrane systems and some systems with low water content. 
  We will observe how the radial density of monomer components and water 
  change within the oore based on membrane water content.

  % BJC: I don't really explicity comment on the partitioning of solutes
  % out of the pore. Maybe I can add some sort of chart. Need to think more.
  % MRS2: it should be mentioned somewhere, probably worth a paragraph or so.  
  % If WATER is much slower outside of the pores, everything else will be slow as well, so we can
  % justify transport there not being interesting
  %Then we will present 
  We then present
  our efforts to understand how small molecules, 
  including water, partition within the pores. From a macroscopic perspective,
  it is straightforward to hypothesize that the water and polar solutes spend
  their time exclusively in the tube-like hydrophilic pore region. Our
  previous work showed that there is a gradual compositional transition from
  the hydrophilic to the hydrophobic region which means that solutes may not
  necessarily stay confined to the centers of the pores or even within the 
  pore region. 
  %MRS2:
  %We will 
  We then study the gradient in composition of solutes and 
  water and any resultant influence it might have on mechanistic properties.
  %MRS2: tweak
  %Finally, and for the bulk of this work, we will 
  For the remainder of the paper, we 
  present our observations 
  and explanations of the observed transport mechanisms exhibited by water
  and solutes. Given that the pores will restrict motion of the solutes, we
  anticipate that transport will be hindered in some way.

  %MRS2: next line is a statement about what we want to do, not what we did?
  %We want to understand
  We investigate
  the differences in solute motion, specifically its mean squared displacement 
  (MSD), based on a solute's size, shape and chemical functionality. We will 
  study the interactions between solutes, the membrane, and water in order to
  determine which mechanism or mechanisms dominate.

@@

  Stable H\textsubscript{II} phases, assembled with Na-GA3C11, can be formed
  using a broad range of water concentrations. In the literature, the system 
  studied in this work is typically synthesized with close to 10 wt\% water.
  \cite{smith_ordered_1997, zhou_new_2007} However, Resel et al. noted that the
  system is likely fully hydrated with less than 7 wt\% water.~\cite{resel_h2-phase_2000}
  Excess water fills space between hexagonal mesophases. We decided to test 
  systems with two different water contents: 5 and 10 wt\%.

  We observed that water partitions into the distal tail region of our system and therefore
  built our initial configurations with water in both regions, close to the expected
  equilibrium partition. We define the distal tail region to be ca. 1.5 nm from the pore
  center based on the minimum in the radial distribution of water
  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
  may or may not be experimentally consistent but it is necessary for our results to be 
  thermodynamically consistent. We iteratively adjusted the pore radius in our systems
  until the appropriate amount of water fit in the pores after running the GROMACS command
  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
  in random locations with a short energy minimization between each insertion. When 
  studying transport of water in the pores, we limited the calculations to water molecules
  that spent greater than 95\% of their time outside of the distal tail region.

@@

  The $z$-direction MSD of water in the 10 wt\% system is linear. Therefore, for
  the purpose of comparison, we calculated its diffusion constant by fitting a line
  to the linear region of the MSD curve.~\cite{maginn_best_2018}. The diffusion constant
  is then equal to $m/2$ where $m$ is the slope of the linear fit. The slope is divided
  by 2 (rather than 6) because we only measured the diffusion coefficient in one 
  dimension.

@@

  Since we will be using this equation for primarily qualitative observations, 
  we made a number of simplifying assumptions so that it could easily be used for 
  comparison between systems. First, we assume that all systems' viscosities
  are equal since we only make minor changes to the membrane's composition and
  accurately assessing the viscosity in a complex and inhomogeneous system such 
  as ours is a challenge by itself. Second, we assume all particles are approximately
  spherical, neglecting the effect of solute shape on mobility. Chan et al. 
  showed that the difference in diffusion constants of differently shaped 
  particles, with constant molecular volume, did not differ by more than 25\%
  with most deviating by less than 10\%.~\cite{chan_effects_2015}. 
  Third, we assume that the ratio of solute and solvent radii as calculated using the
  methodology of Section~\ref{method:molecular_size}, is equivalent to the the 
  ratio of hydrodynamic radii. For similarly shaped molecules, it has been shown that
  one can relate the hydrodynamic radius and radius of gyration (R\textsubscript{g})
  using a constant scaling factor. \cite{lee_molecular_2008,he_novel_2003,li_critical_2009}.
  % BJC: could just calculate Rg instead of end-to-end
  Assuming that our end-to-end distance reasonably approximates R\textsubscript{g} 
  for our small, relatively inflexible molecules, we believe this assumption is 
  justified for qualitative demonstrations relevant to this study.

@@

  Using our procedure we found that sodium ions in a solution of TIP3P water
  coordinate with an average of 3.6 water molecules. We created a 4 x 4 x 4
  nm cubic box of water with the GROMACS tool, \texttt{gmx solvate}. We used
  \texttt{gmx genion} to replace water molecules with sodium and chloride 
  ions in order to create a 0.1 M NaCl solution. We let the system simulate
  for 5 ns and reported the average number of coordinated water molecules 
  per frame after discarding the first nanosecond of simulation.

@@

  We measured the average radial distance of each solute of interest 
  from the pore centers. We binned the radial distances and then 
  normalized by the volume of the annulus defined by the bin edges.
  Although the pores are often described as straight, they have a
  small degree of tortuosity which disrupts the RDF calcuation. We 
  tried to mitigate the effects of tortuosity by calculating the RDF
  with respect to splines that run through the pore centers. See
  Section~\ref{S-section:splines} of the Supporting Information for 
  a graphical illustration. Each spline consists of 10 points, equally
  spaced in the $z$-direction, whose ($x$, $y$) coordinates are defined
  based on the center of mass of all head groups closest, in $z$, to the
  given point. When calculating RDFs, the radial distance from the pore 
  center is based on the distance between the solute center-of-mass and
  the linearly interpolated ($x$, $y$) coordinates of the pore center 
  calculated based on the closest two spline points. Using the splines, 
  % BJC: below to supporting?
  we calculated the tortuosity of the pores by calculating the ratio 
  $\dfrac{L}{Z}$ where $L$ is the length of the spline and $Z$ is the 
  length of the unit cell in the $z$-direction. The average tortuosity
  of each pore is 1.03 $\pm$ 0.01 and 1.07 $\pm$ 0.02 in the 5 and 10 wt\%
  water systems respectively.

  In all RDF plots, we include the average RDF of the head groups as
  a reference. The head group RDF shown is the average of the head 
  group RDFs for each solute system in the plot. We generated 
  95\% confidence intervals by bootstrapping the RDF of each individual
  head group. For each head group, we obtained an RDF averaged over the
  entire simulation trjaectory. We randomly chose head group RDFs with replacement
  and averaged them for each bootsrap trial. This approach assumes that
  head group positions are uncorrelated.

@@

  In contrast to our previous work with a dry version of this 
  membrane, the pore region of the 5 and 10 wt\% water 
  systems are primarily filled with water and sodium ions. We define the
  pore region based on the average COM position of the monomer head groups' 
  % BJC: not sure the best place in paper to define pore region. Maybe a system definitions section in Methods.
  % BJC: need to decide on exact definition. Should probably be the same as the 'Head Groups' line
  carboxylate oxygen atoms. Figure~\ref{fig:component_densities} plots the RDF of each membrane
  constituent in the dry system as well as the 5 and 10 wt\% water systems. 
  In dry systems, the pore center is densely filled with sodium ions and head
  groups. The peak head group density occurs within 0.25 nm of the pore center.
  In hydrated systems, water occupies, and is densest, at the center of each 
  pore. The density of sodium ions is somewhat uniform in the pore center of
  the 5 wt\% water system while it shows a maximum closer to the head groups
  in the 10 wt\% water system. The peak density of sodium ions is not at the
  pore center in the 10 wt\% water system likely because they are still
  loosely associated with the monomer's carboxylate head groups.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_dry.pdf}
  %BJC: simulation is extended to smooth out these curves
  \caption{Dry System}\label{fig:component_density_dry}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \vspace{-0.5cm}
  \includegraphics[width=\textwidth]{monomer_color_coded.pdf}
  \label{fig:monomer_color_coded}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}
  %MRS2: interesting that the head group max is near the transition point where water/tail groups 
  \caption{The radial densities of various monomer components paint a 
  picture of the pore topology where the pore centers are primarily composed
  of water and sodium ions. The monomer groups labeled in each plot correspond to 
  the color-coded monomer pictured in the upper right corner of the figure. 
  All RDFs represent the number of atoms located at a given distance from the
  pore center normalized by the volume of the annular bin to which they belong.
  (a) In the dry system, the density of head groups and sodium ions are highest
  within 0.25 nm of the pore center. (b) In the 5 wt\% system, monomer head 
  groups retreat about 0.2 nm radially in order to make room for water molecules.
  (c) Monomers in the 10 wt\% system retreat an additional 0.2 nm to make room
  for more water.}\label{fig:component_densities}
  \end{figure}

  There is an appreciable amount of water that partitions into the distal tail
  region of both systems. 28\% and 31\% of the total water is present in the tail
  regions of the 5 and 10 wt\% water systems respectively. See 
  Section~\ref{S-section:water_content_equil} of the Supporting Information for more details. This 
  result is due to a combination of the lower density of the tail region
  as well as oxygen atoms at the ends of each monomer tail which can further 
  stabilize water molecules. See Figure~\ref{S-fig:total_density} of the 
  Supporting Information for a graphical illustration of this point.

@@

  Water and sodium's mobilities increase in larger and less crowded pores. 
  In the 10 wt\% water system, the MSD of water is about 51 times higher and
  the MSD of sodium is about 49 times higher compared to the 5 wt\% water system. 
  In the 10 wt\% water system, water moves about 51 times faster than sodium 
  and in the 5 wt\% system, water moves about 49 times faster than sodium. Assuming
  long timescale Brownian behavior of water in the 10 wt\% system, we measured its
  diffusivity to be $7.45 \times 10^{-7}$cm$^2$ / s which is only 1.4\% that of bulk TIP3P 
  water.~\cite{mahoney_diffusion_2000} %BJC: 7.45e-07 versus 5.19e-05 cm^2/s

  % Plots generated with msd_curves.py in figures folder
  % BJC: I show up to 400 ns time lag. Any reason to show full 1000 ns?
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{water_msd_comparison.pdf}
  \caption{Water}\label{fig:water_msd_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{na_msd_comparison.pdf}
  \caption{Sodium Ions}\label{fig:na_msd_comparison}
  \end{subfigure}
  \caption{(a) The MSD of water in the 10 wt\% water system is about 51 times
  higher than water in the 5 wt\% water system. (b) The MSD of sodium in the
  10 wt\% water system is about 49 times higher than sodium in the 5 wt\% 
  water system.}\label{fig:msd_comparison}
  \end{figure}
